Clustering based on probability distributions with application on residential customers

### 2021-10-20 main.Rmd
graphs look better

```{r interaction-gran, fig.cap = "Design-1 has no change in distributions across different categories of $g1$ or $g2$, while Design-2 and Design-3 change across only $g1$ and $g2$ respectively. Design-4 changes across categories of both $g1$ and $g2$."}

>>>>

```{r interaction-gran, fig.cap = "Design-1 (a) has no change in distributions across different categories of $g1$ or $g2$, while Design-2 (b) and Design-3 (c) change across only $g1$ and $g2$ respectively. Design-4 (d) changes across categories of both $g1$ and $g2$."}
